Dynein project log

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Make stepping data files slightly prettier.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ $ steps / second & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & ??      & & keeled over after ns \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & & no error yet\\\hline
  \end{tabular}
\end{center}

If the mean stepping rate from Weihong's paper is ~ 1 step / .1 seconds, then at a dt of $1e-11$s would lead to a desired unbinding
probability of $1e-11/.1 = 1e-10$.
